\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
{\LARGE Young-Ik Kim}\\[0.5em]
AI Lab, DenComm Inc.,\\
Tel: +82-10-4400-5643\\
E-mail: \href{mailto:kim.youngik@gmail.com}{kim.youngik@gmail.com}
\end{center}

\section*{Research Interests}
\begin{itemize}[leftmargin=*]
\item Multimodal LLM, Speaker-aware reasoning, GraphRAG
\item Speech recognition, synthesis and translation
\item Speech detection, separation and enhancement
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*]
\item Ph.D.\ in Applied Mathematics, Korea Advanced Institute of Science and Technology (Feb. 2007)\\
Thesis: ``Spatial Hearing Algorithms Based on Binaural Zero-Crossings: Sound Source Localization, Segregation, and Dereverberation.'' (Advisor: Rhee Man Kil)
\item M.A.\ in Applied Mathematics, Korea Advanced Institute of Science and Technology (Feb. 2003)\\
Thesis: ``Source Localization Algorithms in Binaural Processing Models.'' (Advisor: Rhee Man Kil)
\item M.A.\ in Control and Instrumentation, Korea Maritime University (Feb. 1999)\\
Thesis: ``Facial Information Extraction Using Principal Component Analysis.'' (Advisor: Seok Je Cho)
\item B.A.\ in Control and Instrumentation, Korea Maritime University (Feb. 1997)
\end{itemize}

\section*{Job Experience}
\begin{itemize}[leftmargin=*]
\item AI Research Engineer, AI Lab, DenComm (Aug. 2023 -- Present)\\
Research area: Automatic speech recognition, speech synthesis
\item AI Research Engineer, NCSOFT (Jan. 2016 -- Jul. 2023)\\
Research area: Automatic speech recognition, speech translation, speech synthesis
\item AI Research Scientist, ETRI (Sep. 2007 -- Dec. 2015)\\
Research area: Automatic speech recognition, speech translation, speech synthesis
\item Post Doctoral Researcher, School of Information Technology, KAIST (Apr. 2007 -- Present)\\
Research area: Integration of artificial brain systems, mechanisms for brain information processing of auditory and visual systems
\item Part-Time Lecturer, KAIST IT Academy (Jan. 2006 -- Feb. 2007)\\
Course: Matlab Programming
\item Post Master Researcher, Brain Science Research Center, KAIST (Feb. 1999 -- Feb. 2001)\\
Research area: Modeling of auditory pre-processor for robust speech recognition
\end{itemize}

\section*{Publications}

\subsection*{Journals}
\begin{itemize}[leftmargin=*]
\item Young-Sun Joo, Hanbin Bae, Young-Ik Kim, Hoon-Young Cho, Hong-Goo Kang, ``Effective Emotion Transplantation in an End-to-End Text-to-Speech System,'' \textit{IEEE Access}, 8, September 2020.
\item Sung Jun An, Rhee Man Kil, Young-Ik Kim, ``Zero-crossing-based speech segregation and recognition for humanoid robots,'' \textit{IEEE Transactions on Consumer Electronics}, 55(3), October 2009.
\item Young-Ik Kim and Rhee Man Kil, ``Estimation of Inter-aural Time Differences Based on Zero-Crossings in Noisy Multi-Source Environments,'' \textit{IEEE Transactions on Audio, Speech and Language Processing}, 15(2), pp.~734--743, 2007. (SCI)
\item Young-Ik Kim, Sung Jun An, Rhee Man Kil and Hyung-Min Park, ``Zero-Crossing Based Time-Frequency Masking for Sound Segregation,'' \textit{Neural Information Processing -- Letters and Reviews}, 10(4--6), pp.~125--134, 2006. (International)
\item Rhee Man Kil and Young-Ik Kim, ``Tree-Structure Filter-Banks for Noise-Robust Speech Recognition,'' \textit{Korean Journal of Brain Science and Technology}, 1(1), pp.~139--147, 2001. (Domestic)
\end{itemize}

\subsection*{International Conferences and Workshops}
\begin{itemize}[leftmargin=*]
\item Jinhyeok Yang, Jae-Sung Bae, Taejun Bak, Young-Ik Kim, Hoon-Young Cho, ``GANSpech: Adversarial Training for High-Fidelity Multi-Speaker Speech Synthesis,'' \textit{INTERSPEECH 2021}, September 2021.
\item Taejun Bak, Jae-Sung Bae, Hanbin Bae, Young-Ik Kim, Hoon-Young Cho, ``FastPitchFormant: Source-filter based Decomposed Modeling for Speech Synthesis,'' \textit{INTERSPEECH 2021}, September 2021.
\item Gyeong-Hoon Lee, Tae-Woo Kim, Hanbin Bae, Min-Ji Lee, Young-Ik Kim, Hoon-Young Cho, ``N-Singer: A Non-Autoregressive Korean Singing Voice Synthesis System for Pronunciation Enhancement,'' \textit{INTERSPEECH 2021}, September 2021.
\item Hanbin Bae, Jae-Sung Bae, Young-Sun Joo, Young-Ik Kim, Hoon-Young Cho, ``A Neural Text-to-Speech Model Utilizing Broadcast Data Mixed with Background Music,'' \textit{ICASSP 2021}, June 2021.
\item Jinhyeok Yang, Junmo Lee, Young-ik Kim, Hoon-Young Cho, Injung Kim, ``VocGAN: A High-Fidelity Real-time Vocoder with a Hierarchically-nested Adversarial Network,'' \textit{INTERSPEECH 2020}, September 2020.
\item Young-Ik Kim, Hoon-Young Cho, Sang-Hun Kim, ``Zero-Crossing-Based Channel Attentive Weighting of Cepstral Features for Robust Speech Recognition: The ETRI 2011 CHiME Challenge System,'' \textit{INTERSPEECH 2011}, September 2011.
\item Sung Jun An, Young-Ik Kim, and Rhee Man Kil, ``Zero-Crossing-Based Ratio Masking for Sound Segregation,'' \textit{INTERSPEECH 2007}, Antwerp, Belgium, August 27--31, 2007. 
\item Young-Ik Kim, Sung Jun An, and Rhee Man Kil, ``Zero-Crossing Based Binaural Mask Estimation For Missing Data Speech Recognition,'' \textit{IEEE International Conference on Acoustics, Speech and Signal Processing}, Toulouse, France, May 2006. 
\item Young-Ik Kim, and Rhee Man Kil, ``Sound Segregation Based on Binaural Zero-Crossing Peak-Amplitude Coding,'' \textit{INTERSPEECH 2005 -- 9th European Conference on Speech Communication and Technology}, Lisbon, Portugal, September 2005. 
\item Young-Ik Kim, and Rhee Man Kil, ``Noise-robust estimation of sound source directions based on zero-crossing peak-amplitude coding,'' \textit{8th International Conference on Cognitive and Neural Systems}, Boston University, USA, May 2004. 
\item Rhee Man Kil, Young-Ik Kim, Hwa Kil Kim, Seong Ho Kim, and Sung Ho Kim, ``A Design of Noise-Robust Speech-Front-End Based on Tree-Structured Filter-Bank,'' \textit{ICONIP 2000 -- 7th International Conference on Neural Information Processing}, Daejeon, Korea, November 2000. 
\item Rhee Man Kil, Young-Ik Kim, and Geon Hyung Lee, ``A Noise-Robust Front-End Based on Tree-Structured Filter-Bank for Speech Recognition,'' \textit{IEEE International Joint Conference on Neural Networks}, Como, Italy, July 2000. 
\end{itemize}

\end{document}